# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r, echo=TRUE}
activity = read.csv("activity.csv")
activity$date <- as.Date(activity$date)

activityDaily <- as.data.frame(table(activity$date))
colnames(activityDaily) <- c("date", "steps")
activityDaily$date <- as.Date(activityDaily$date)

for (i in 1:nrow(activityDaily)) {
    curActivity <- subset(activity, activity$date == activityDaily$date[i])
    activityDaily$steps[i] <- sum(curActivity$steps, na.rm=TRUE)
}
    
activity5min <- as.data.frame(table(activity$interval))
colnames(activity5min) <- c("interval", "steps")

for (i in 1:nrow(activity5min)) {
  curActivity = subset(activity, activity$interval == activity5min$interval[i])
  activity5min$steps[i] <- mean(curActivity$steps, na.rm=TRUE)
}
```

## What is mean total number of steps taken per day?
### Make a histogram of the total number of steps taken each day
```{r, echo=TRUE}
  barplot(activityDaily$steps, names.arg = activityDaily$date, xlab = "Date", ylab = "Steps")
```

### Calculate and report the mean and median total number of steps taken per day
```{r, echo=TRUE}
    mean(activityDaily$steps, na.rm=TRUE)
    median(activityDaily$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?
### Time series plot (i.e. type = "l") of the 5-minute interval (x-axis)
```{r, echo=TRUE}
plot(activity5min$steps, type="l")
```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
activity5min$interval[which.max(activity5min$steps)]
```

## Imputing missing values
### Calculate and report the total number of missing values in the dataset
```{r, echo=TRUE}
sum(is.na(activity$steps))
```

### Impute the dataset
```{r, echo=TRUE}
activityImputed <- activity
activityImputed$date <- as.Date(activityImputed$date)
naIdx <- is.na(activity$steps)
activityImputed$steps[naIdx] <- mean(activity$steps, na.rm=T)

activityDailyImp <- as.data.frame(table(activityImputed$date))

colnames(activityDailyImp) <- c("date", "steps")

activityDailyImp$date <- as.Date(activityDailyImp$date)

for (i in 1:nrow(activityDailyImp)) {
    curActivity <- subset(activityImputed, activityImputed$date == activityDailyImp$date[i])
    activityDailyImp$steps[i] <- sum(curActivity$steps, na.rm=TRUE)
}

barplot(activityDailyImp$steps, names.arg = activityDailyImp$date, xlab = "Date", ylab = "Steps")

```

###  Calculate and report the mean and median total number of steps taken per day.
```{r, echo=TRUE}    
    mean(activityDailyImp$steps, na.rm=TRUE)
    median(activityDailyImp$steps, na.rm=TRUE)
```
    
## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}


```
